Modeling Univariate and Multivariate Stochastic Volatility in \proglang{R} with \stochvol{} and \factorstochvol

### 2021-05-07 article2.Rnw
update article; remove some dependencies; regenerate manual

<<setup, include=FALSE, cache=FALSE>>=
knitr::render_sweave()
knitr::opts_chunk$set(prompt = TRUE,
                      fig.show = "hide",
                      warning = FALSE,
                      error = FALSE,
                      message = FALSE,
                      echo = FALSE,
                      cache = FALSE,
                      fig.path = "Figures/jss3813-",
                      tidy = FALSE)
base::options(continue = "+  ", prompt = "R> ", width = 70,
  useFancyQuotes = FALSE)
@

@@

As mentioned earlier, the sampling algorithms for the latent states $\hvec$ in \stochvol{} rely on a Gaussian mixture approximation as in~\citet{omori2007stochastic} and~\citet{kastner2014ancillarity}.
The approximation tends to be very good, therefore the default setting is not to correct for model misspecification.
However, this correction can be enabled in all of the sampling routines through the \code{expert} argument as shown for \fct{svsample} in the following.
<<results='hide'>>=
y <- svsim(50)$y
svsample(y, expert = list(correct_model_misspecification = TRUE))
@

@@

\bibliography{ref2}

>>>>

<<setup, include=FALSE, cache=FALSE>>=
knitr::render_sweave()
knitr::opts_chunk$set(prompt = TRUE,
                      fig.show = "hide",
                      warning = FALSE,
                      error = FALSE,
                      message = FALSE,
                      echo = FALSE,
                      cache = FALSE,
                      fig.path = "Figures/jss3813-",
                      tidy = FALSE)
base::options(continue = "+  ", prompt = "R> ", width = 70,
  useFancyQuotes = FALSE)

library("RColorBrewer")
library("LSD")
library("zoo")
@

@@

As mentioned earlier, the sampling algorithms for the latent states $\hvec$ in \stochvol{} rely on a Gaussian mixture approximation as in~\citet{omori2007stochastic} and~\citet{kastner2014ancillarity}.
The approximation tends to be very good, therefore the default setting is not to correct for model misspecification.
However, this correction can be enabled in all of the sampling routines through the \code{expert} argument as shown for \fct{svsample} in the following.
<<results='hide'>>=
set.seed(3)
y <- svsim(50)$y
svsample(y, expert = list(correct_model_misspecification = TRUE))
@

@@

\bibliography{ref}
